---
title: "Assignment 5 suraj gadapa"
author: "suraj gadapa"
date: "2022-11-15"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(cluster)
library(caret)
library(dendextend)
library(factoextra)
```

```{r}
c<-read.csv("C:/Users/suraj/Downloads/Cereals.csv")
c<- na.omit(c)
head(c)
```

#Normalizing the dataset
```{r}
c<- c[,4:16]
c <- scale(c,center = TRUE,scale = TRUE)
head(c)
```

#Task-1.Apply hierarchical clustering to the data using Euclidean distance to the normalized measurements. 
#Use Agnes to compare the clustering from single linkage, complete 
#linkage, average linkage, and Ward. Choose the best method.
```{r}
Euclidean_Dist <- dist(c, method = "euclidean")
# Hierarchical clustering using Complete Linkage
cl1 <- hclust(Euclidean_Dist, method = "complete" )
# Plot the obtained dendrogram
plot(cl1, cex = 0.6, hang = -1)
round(cl1$height, 3)
```

# Compute with agnes and with different linkage methods
```{r}
cl_single <- agnes(c, method = "single")
print(cl_single$ac)
cl_complete <- agnes(c, method = "complete")
print(cl_complete$ac)
cl_average <- agnes(c, method = "average")
print(cl_average$ac)
cl_ward <- agnes(c, method = "ward")
print(cl_ward$ac)
```
#The agglomerative coefficient obtained by Ward's method is the largest. 

#visualizing  the dendrogram
```{r}
cl_Ward <- agnes(Euclidean_Dist, method = "ward")
pltree(cl_Ward, cex = 0.6, hang = -1, main = "Dendrogram of agnes for ward") 
```
#Task-2.How many clusters would you choose?
```{r}
#The largest difference in height can be used to determine the k value, hence K =5 is the best option.
cl_Ward <- hclust(Euclidean_Dist,method = "ward.D2")
clust_comp <- cutree(cl_Ward, k=5)
table(clust_comp)
plot(cl_Ward,cex=0.6)
rect.hclust(cl_Ward, k = 5, border = 2:10,)
Temp <- cbind(as.data.frame(cbind(c,clust_comp)))
#Visualizing the clusters in Scatter plot
fviz_cluster(list(data=Euclidean_Dist, cluster = clust_comp))
```

#Task-3.The elementary public schools would like to choose a set of cereals to include in their
#daily cafeterias. Every day a different cereal is offered, but all cereals should support a
#healthy diet. For this goal, you are requested to find a cluster of “healthy cereals.”
```{r}
Healthy_cereal <- na.omit(read.csv("C:/Users/suraj/Downloads/Cereals.csv"))
Healthy_cereal<- cbind(Healthy_cereal,clust_comp)
mean(Healthy_cereal[Healthy_cereal$clust_comp==1,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==2,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==3,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==4,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==5,"rating"])
```


Cluster1 has the highest rating (73.84446), so we'll choose it as a healthy cereal.
